Together, Individuals Make a Difference

### 2025-01-26 论文/PAPER.tex
上传了图片
流程图

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{Percentage of Medals of Different Sports in China.svg}
%	\caption{Flow Chart of Our Work}
%	\label{img}
%\end{figure}
	\caption{The result of Model 2}\label{fig:result}
\end{figure}
%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\Percentage of Medals of Different Sports in China.svg"
%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\每届奥运会新增和退役的人数.png"
%"C:\Users\于灏文1\Desktop\2025_codium_veritas_2506135\论文\img\water.png"
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{water.png}
	\caption{The result of Model 2}\label{fig:result}
\end{figure}
\begin{enumerate}[\bfseries 1.]
    \item We do ...
    \item We do ...
    \item We do ...
\end{enumerate}

@@

\section{Notations}
The primary notations used in this paper are listed in Table \ref{tb:notation}.

% 三线表示例
\begin{table}[!htbp]
\begin{center}
\caption{Notations}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	$\sum m_{c_{i} S_{j}}$ &the last one\\
	\bottomrule
\end{tabular}\label{tb:notation}
\end{center}
\end{table}

\section{Data Preprocessing}
\subsection{Basic Data Preprocessing}
\subsection{Data Mining}
\section{Task1:}
\subsection{Details about Model 1}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

>>>>

%图片示例（water.png）
%\begin{figure}[htbp]
%	\centering
%	\includegraphics[width=.8\textwidth]{water.png}
%	\caption{The result of Model 2}\label{fig:result}
%\end{figure}
\begin{enumerate}[\bfseries 1.]
    \item We do ...
    \item We do ...
    \item We do ...
\end{enumerate}

@@

\section{Notations}

The primary notations used in this paper are listed in Table \ref{tb:notation}.

% 三线表示例
\begin{table}[!htbp]
\begin{center}
\caption{Notations}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$C_{i}$&the first one\\
	$S_{i}$&the second one\\
	$G$&the second one\\
	$V$&the second one\\
	$B$&the second one\\
	$M$&the second one\\
	$A$&the second one\\
	$D$&the second one\\
	$E$&the second one\\
%	$\alpha$ &the last one\\
    $\gamma$&Sport Advantagen Coefficient\\
  	$ m_{c_{i}}$ &the second one\\
	$ m_{c_{i} s_{j}}$ &the second one\\
    $g_{i}$&the second one\\
    $\xi$&The Probability of First Medal\\
	\bottomrule
\end{tabular}\label{tb:notation}
\end{center}
\end{table}

\section{Data Preprocessing}
\subsection{Basic Data Preprocessing}

$$G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X$$

\begin{figure}[htbp]
	\centering
	\includegraphics[width=12cm]{img/Level1.png}
	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
	\label{fig:aa}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=12cm]{img/Level2.png}
	\caption{aa}
	\label{fig:aa}
\end{figure}

\subsection{Data Mining}
\section{Task1:}
\subsection{Details about Model 1}
The detail can be described by equation \eqref{eq1}:\autoref{eq1}:
%带标签的方程
\begin{equation}\label{eq1}
\alpha+\beta=\gamma
\end{equation}
%不带标签的方程
\[
\alpha+\beta=\gamma
\]
$$\alpha$$

%$$ \gamma=\frac{$m_{c_{i} s_{j}}$}{$\sum m_{c_{i} s_{j}}$ }$$

%\[
%\gamma = \frac{$m_{c_i s_j}$}{$\sum m_{c_i s_j}$}
%\]
\[
\gamma = \frac{m_{c_i s_j}}{\sum m_{c_i s_j}}
\]
